---
title: "PhIP-seq Targeted Peptide Analysis"
subtitle: "`r readRDS(params$rds_path)$antigen` homology subset"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    theme: flatly
    highlight: tango
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    toc_depth: 3
    self_contained: true
params:
  rds_path: ""
---

```{css, echo=FALSE}
body { font-size: 14px; }
h1, h2, h3 { color: #2c3e50; }
.section-intro { color: #555; margin-bottom: 1em; font-style: italic; }
.stat-box {
  display: inline-block; padding: 12px 20px; margin: 6px;
  border-radius: 6px; text-align: center; min-width: 130px;
  background: #ecf0f1;
}
.stat-box .num { font-size: 1.8em; font-weight: bold; color: #2980b9; }
.stat-box .lbl { font-size: 0.85em; color: #7f8c8d; }
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE,
  fig.width = 10, fig.height = 5.5
)
pkgs <- c("data.table", "ggplot2", "dplyr", "tidyr", "knitr",
          "kableExtra", "scales")
invisible(lapply(pkgs, function(p) library(p, character.only = TRUE)))

d  <- readRDS(params$rds_path)
g1 <- d$group1; g2 <- d$group2; g3 <- d$group3

grp_cols <- c(setNames("#c0392b", g1),
              setNames("#2980b9", g2),
              setNames("#27ae60", g3))

theme_report <- function()
  theme_bw(base_size = 11) +
  theme(panel.grid.minor = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5),
        legend.position = "bottom")

# Ensure comp$group is a factor with cases first
d$comp$group <- factor(d$comp$group, levels = c(g1, g2, g3))

stat_box <- function(n, lbl)
  sprintf('<div class="stat-box"><div class="num">%s</div><div class="lbl">%s</div></div>', n, lbl)
```

::: {.section-intro}
This report summarises a targeted analysis of **`r length(d$present_ids)`
peptides** with homology to **`r d$antigen`**, comparing **`r g1`** (cases)
against **`r g2`** and **`r g3`** at a Z-score threshold of **`r d$zscore`**,
sex filter = **`r if (nchar(d$sex) == 0) "both sexes" else d$sex`**.

The analysis is independent of the genome-wide regression and asks two
questions:
*(1) which individual peptides differ between groups within this subset,*
and *(2) does the overall reactivity to `r d$antigen` differ between groups
when aggregated across the subset?*
:::

```{r overview-stats, results='asis'}
cat(stat_box(length(d$present_ids), "peptides analysed"))
cat(stat_box(length(d$missing_ids), "peptides missing"))
cat(stat_box(nrow(d$comp),          "subjects"))
cat("\n\n")
if (length(d$missing_ids) > 0) {
  cat("\n> **Note:** ", length(d$missing_ids),
      " peptide ID(s) from the input list were not found on all plates and were excluded: ",
      paste(d$missing_ids, collapse = ", "), "\n", sep = "")
}
```

---

# 1 · Composite scores per subject

::: {.section-intro}
For each subject, two composite measures of overall reactivity to
**`r d$antigen`** are computed across the `r length(d$present_ids)`-peptide
subset:

- **Count of peptides hit** — number of peptides above Z = `r d$zscore`
- **Mean Z-score** — average reactivity across all subset peptides
  (regardless of whether they cross the hit threshold)

These ask whether *overall* reactivity to the antigen differs between groups —
useful when individual peptides have low power on their own.
Kruskal-Wallis tests the three groups together; pairwise Wilcoxon tests
the case vs. each control.
:::

```{r composite-helper, include=FALSE}
composite_plot <- function(df, ycol, ylab, title) {
  k <- kruskal.test(df[[ycol]] ~ df$group)
  pw <- pairwise.wilcox.test(df[[ycol]], df$group,
                             p.adjust.method = "none", exact = FALSE)
  # Extract two case-vs-control p-values
  p_g2 <- tryCatch(pw$p.value[g2, g1], error = function(e) NA)
  p_g3 <- tryCatch(pw$p.value[g3, g1], error = function(e) NA)

  subtitle <- sprintf(
    "Kruskal-Wallis p = %.3g  |  %s vs. %s: p = %.3g  |  %s vs. %s: p = %.3g",
    k$p.value, g2, g1, p_g2, g3, g1, p_g3)

  ggplot(df, aes(x = group, y = .data[[ycol]], fill = group)) +
    geom_violin(alpha = 0.4, scale = "width", linewidth = 0.3) +
    geom_boxplot(width = 0.15, outlier.shape = NA, alpha = 0.85,
                 linewidth = 0.4) +
    geom_jitter(width = 0.12, height = 0, size = 1.4, alpha = 0.6,
                colour = "grey20") +
    scale_fill_manual(values = grp_cols, guide = "none") +
    labs(title = title, subtitle = subtitle, x = NULL, y = ylab) +
    theme_report() +
    theme(axis.text.x = element_text(size = 11, face = "bold"))
}
```

## Number of peptides hit

```{r composite-count, fig.height=5}
composite_plot(d$comp, "n_hit",
               paste0("Number of ", d$antigen, " peptides hit (Z > ", d$zscore, ")"),
               paste0("Per-subject hit count over the ",
                      length(d$present_ids), "-peptide subset"))
```

## Mean Z-score across the subset

```{r composite-meanz, fig.height=5}
composite_plot(d$comp, "mean_z",
               paste0("Mean Z-score across ", d$antigen, " peptides"),
               paste0("Per-subject mean Z over the ",
                      length(d$present_ids), "-peptide subset"))
```

## Summary table

```{r composite-table}
d$comp %>%
  group_by(group) %>%
  summarise(
    n               = n(),
    `Mean # hits`   = round(mean(n_hit, na.rm = TRUE), 2),
    `Median # hits` = round(median(n_hit, na.rm = TRUE), 2),
    `Mean Z`        = round(mean(mean_z, na.rm = TRUE), 3),
    `Median Z`      = round(median(mean_z, na.rm = TRUE), 3),
    `Max Z (avg)`   = round(mean(max_z, na.rm = TRUE), 3),
    .groups = "drop"
  ) %>%
  rename(Group = group) %>%
  kable(align = "lrrrrrr") %>%
  kable_styling(bootstrap_options = c("striped","condensed"),
                full_width = FALSE, font_size = 12) %>%
  column_spec(1, bold = TRUE)
```

---

# 2 · Per-peptide regression

::: {.section-intro}
Multinomial logistic regression (same model as the genome-wide analysis),
restricted to the `r length(d$present_ids)`-peptide subset. With many fewer
tests, the FDR burden is much lower — even modest p-values can be meaningful.
:::

## Frequency comparison

```{r perpep-freq, fig.height=min(25, max(4, 0.3 * min(length(d$present_ids), 80)))}
# Cap the number of peptides shown on the bar chart to avoid generating
# an unrenderably tall figure.  When the subset is large, show the top 80
# by min p-value (per_pep is already sorted by pval_min ascending).
n_show <- min(length(d$present_ids), 80)
freq_src <- head(d$per_pep, n_show)
freq_long <- freq_src %>%
  mutate(label = paste0(peptide, " — ", species)) %>%
  select(label, peptide,
         !!g1 := all_of(paste0("freq_", g1)),
         !!g2 := all_of(paste0("freq_", g2)),
         !!g3 := all_of(paste0("freq_", g3))) %>%
  pivot_longer(c(g1, g2, g3), names_to = "group", values_to = "freq") %>%
  mutate(group = factor(group, levels = c(g1, g2, g3)),
         label = factor(label, levels = rev(unique(label))))

ggplot(freq_long, aes(x = label, y = freq, fill = group)) +
  geom_col(position = position_dodge(0.7), width = 0.65) +
  scale_fill_manual(values = grp_cols, name = NULL) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     expand = expansion(mult = c(0, 0.08))) +
  coord_flip() +
  labs(title = paste0("Per-group hit frequency (Z > ", d$zscore, ")"),
       subtitle = if (n_show < length(d$present_ids)) {
                    paste0("Top ", n_show, " of ", length(d$present_ids),
                           " ", d$antigen, " peptides, ordered by min p-value")
                  } else {
                    paste(length(d$present_ids), d$antigen,
                          "peptides, ordered by min p-value")
                  },
       x = NULL, y = "Fraction of subjects called positive") +
  theme_report()
```

## Regression results

```{r perpep-table}
g2_vs_g1 <- paste0(g2, "_vs_", g1)
g3_vs_g1 <- paste0(g3, "_vs_", g1)

d$per_pep %>%
  select(Peptide = peptide, Species = species,
         !!paste0("Freq ", g1) := all_of(paste0("freq_", g1)),
         !!paste0("Freq ", g2) := all_of(paste0("freq_", g2)),
         !!paste0("Freq ", g3) := all_of(paste0("freq_", g3)),
         !!paste0("β ", g2_vs_g1) := all_of(paste0("beta_", g2_vs_g1)),
         !!paste0("p ", g2_vs_g1) := all_of(paste0("pval_", g2_vs_g1)),
         `p (g2 FDR)`                 = pval_g2_fdr,
         !!paste0("β ", g3_vs_g1) := all_of(paste0("beta_", g3_vs_g1)),
         !!paste0("p ", g3_vs_g1) := all_of(paste0("pval_", g3_vs_g1)),
         `p (g3 FDR)`                 = pval_g3_fdr) %>%
  mutate(across(where(is.numeric), ~ signif(., 3))) %>%
  kable(align = paste0("ll", strrep("r", 9))) %>%
  kable_styling(bootstrap_options = c("striped","hover","condensed"),
                full_width = FALSE, font_size = 11) %>%
  column_spec(1, bold = TRUE, monospace = TRUE)
```

---

# 3 · Per-subject Z-score heatmap

::: {.section-intro}
Each row is a subject (ordered by group), each column a `r d$antigen`-homologous
peptide (ordered by per-peptide minimum p-value, most significant on the left).
The colour shows the per-subject Z-score (after min-of-duplicates). This view
shows whether group differences come from a handful of peptides hitting a
handful of subjects vs. a broad pattern of reactivity.
:::

```{r heatmap, fig.height=max(6, min(20, 0.18 * nrow(d$comp))), fig.width=max(8, min(14, 1 + 0.18 * min(length(d$present_ids), 100)))}
# Reorder subjects by group then by composite hit count
sub_order <- d$comp %>%
  arrange(group, desc(n_hit)) %>%
  pull(subject)

# Cap heatmap columns at 100 peptides (most significant first) for readability
# and to keep the rendered figure within safe surface dimensions.
n_pep_show <- min(length(d$present_ids), 100)
pep_order  <- as.character(head(d$per_pep$peptide, n_pep_show))

zlong <- as.data.frame(d$zmat[, pep_order, drop = FALSE]) %>%
  tibble::rownames_to_column("subject") %>%
  pivot_longer(-subject, names_to = "peptide", values_to = "z") %>%
  left_join(d$comp[, c("subject", "group")], by = "subject") %>%
  mutate(subject = factor(subject, levels = sub_order),
         peptide = factor(peptide, levels = pep_order))

# Cap Z at 99th percentile so a few extreme outliers don't compress the palette
z_cap <- quantile(zlong$z, 0.99, na.rm = TRUE)
if (!is.finite(z_cap) || z_cap <= 0) z_cap <- 10
zlong$z_capped <- pmin(zlong$z, z_cap)

heatmap_subtitle <- if (n_pep_show < length(d$present_ids)) {
  paste0("Showing top ", n_pep_show, " of ", length(d$present_ids),
         " peptides (ordered by min p-value); rows = subjects")
} else {
  "Rows = subjects, columns = peptides (ordered by min p-value)"
}

# Row annotation strip via facet on group
ggplot(zlong, aes(x = peptide, y = subject, fill = z_capped)) +
  geom_tile() +
  facet_grid(group ~ ., scales = "free_y", space = "free_y", switch = "y") +
  scale_fill_gradientn(
    colours = c("#2c3e50", "#ecf0f1", "#f39c12", "#c0392b"),
    values  = scales::rescale(c(min(zlong$z, na.rm = TRUE),
                                d$zscore,
                                d$zscore * 1.5,
                                z_cap)),
    na.value = "grey90",
    name = paste0("Z (capped @ ", round(z_cap, 1), ")")) +
  labs(title = paste0("Per-subject Z-scores across ", d$antigen, " peptides"),
       subtitle = heatmap_subtitle,
       x = "Peptide ID", y = NULL) +
  theme_report() +
  theme(
    axis.text.x  = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 8),
    axis.text.y  = element_text(size = 7),
    strip.text.y.left = element_text(angle = 0, face = "bold"),
    strip.placement   = "outside",
    panel.spacing.y   = unit(0.15, "lines")
  )
```

---

# 4 · Parameters and output files

```{r params-table}
data.frame(
  Parameter = c("Antigen",
                "Group 1 (cases)",
                "Group 2 (control 1)",
                "Group 3 (control 2)",
                "Z-score threshold",
                "Sex filter",
                "Target peptides supplied",
                "Target peptides analysed",
                "Target peptides missing",
                "Subjects analysed",
                "Output prefix",
                "Report generated"),
  Value = c(d$antigen, g1, g2, g3,
            as.character(d$zscore),
            ifelse(nchar(d$sex) == 0, "both sexes", d$sex),
            as.character(length(d$present_ids) + length(d$missing_ids)),
            as.character(length(d$present_ids)),
            as.character(length(d$missing_ids)),
            as.character(nrow(d$comp)),
            basename(d$output_base),
            format(Sys.time(), "%Y-%m-%d %H:%M"))
) %>%
  kable(align = "ll") %>%
  kable_styling(bootstrap_options = c("striped","condensed"),
                full_width = FALSE, font_size = 12)
```
