---
title: "PhIP-seq Three-Group Summary Report"
subtitle: "`r params$group1` vs. `r params$group2` vs. `r params$group3`"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    theme: flatly
    highlight: tango
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    toc_depth: 3
    self_contained: true
    df_print: paged
params:
  group1:       "PF Patient"
  group2:       "Endemic Control"
  group3:       "Non Endemic Control"
  output_dir:   "./"
  pval_thresh:  0.05
  fdr:          true
  top_n:        20
  label_col_peptide:  "species"
---

```{css, echo=FALSE}
body { font-size: 14px; }
h1, h2, h3 { color: #2c3e50; }
.section-intro { color: #555; margin-bottom: 1em; font-style: italic; }
.stat-box {
  display: inline-block; padding: 12px 20px; margin: 6px;
  border-radius: 6px; text-align: center; min-width: 120px;
  background: #ecf0f1;
}
.stat-box .num  { font-size: 1.8em; font-weight: bold; color: #2980b9; }
.stat-box .lbl  { font-size: 0.85em; color: #7f8c8d; }
.stat-box.red   .num { color: #c0392b; }
.stat-box.green .num { color: #27ae60; }
.stat-box.orange .num { color: #d35400; }
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.width  = 10,
  fig.height = 5.5
)

# ── packages ──────────────────────────────────────────────────────────────────
pkgs <- c("data.table", "ggplot2", "dplyr", "tidyr", "knitr",
          "kableExtra", "scales", "ggrepel", "patchwork", "stringr", "fs")
invisible(lapply(pkgs, function(p) {
  if (!requireNamespace(p, quietly = TRUE))
    stop(paste0("Install required package: ", p))
  library(p, character.only = TRUE)
}))

# ── helpers ───────────────────────────────────────────────────────────────────
g1    <- params$group1
g2    <- params$group2
g3    <- params$group3
odir  <- params$output_dir
alpha <- params$pval_thresh

g2_vs_g1 <- paste0(g2, "_vs_", g1)
g3_vs_g1 <- paste0(g3, "_vs_", g1)

col_freq  <- function(g) paste0("freq_", g)
col_beta  <- function(x) paste0("beta_", x)
col_pval  <- function(x) paste0("pval_", x)
col_se    <- function(x) paste0("se_",   x)

# Find the most recent matching CSV in odir
find_csv <- function(pattern) {
  hits <- list.files(odir, pattern = pattern, full.names = TRUE)
  if (length(hits) == 0) return(NULL)
  hits[order(file.info(hits)$mtime, decreasing = TRUE)][1]
}

read_result <- function(path) {
  if (is.null(path) || !file.exists(path)) return(NULL)
  df <- data.frame(data.table::fread(path, sep = ",", header = TRUE),
                   check.names = FALSE)
  df
}

apply_fdr <- function(df, col) {
  if (params$fdr && col %in% colnames(df))
    df[[col]] <- p.adjust(as.numeric(df[[col]]), method = "BH")
  df
}

prep_result <- function(df) {
  if (is.null(df)) return(NULL)
  for (col in c(col_pval(g2_vs_g1), col_pval(g3_vs_g1)))
    df <- apply_fdr(df, col)
  for (col in colnames(df))
    if (col != "peptide" && col != "species")
      suppressWarnings({ df[[col]] <- as.numeric(df[[col]]) })
  df$pval_min <- pmin(df[[col_pval(g2_vs_g1)]],
                      df[[col_pval(g3_vs_g1)]], na.rm = TRUE)
  df
}

sig_any <- function(df)
  !is.na(df$pval_min) & df$pval_min < alpha

# Shared colour palette
grp_cols <- c(
  setNames("#c0392b", g1),   # red   = cases
  setNames("#2980b9", g2),   # blue  = control 1
  setNames("#27ae60", g3)    # green = control 2
)

contrast_cols <- c(
  setNames("#2980b9", g2_vs_g1),
  setNames("#27ae60", g3_vs_g1)
)

theme_report <- function()
  theme_bw(base_size = 11) +
  theme(panel.grid.minor = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5),
        legend.position = "bottom")

stat_box <- function(n, label, cls = "") {
  glue::glue if (FALSE) NULL   # suppress glue dependency
  sprintf(
    '<div class="stat-box %s"><div class="num">%s</div><div class="lbl">%s</div></div>',
    cls, n, label)
}

# ── load data ─────────────────────────────────────────────────────────────────
pep_file   <- find_csv("Multiplate_Three_Group_Peptide_Comparison")
vscan_file <- find_csv("Multiplate_Three_Group_VirScan_Seropositivity_Comparison")
vfrac_file <- find_csv("Multiplate_Three_Group_VirFrac_Seropositivity_Comparison")

pep_dat   <- prep_result(read_result(pep_file))
vscan_dat <- prep_result(read_result(vscan_file))
vfrac_dat <- prep_result(read_result(vfrac_file))

has_pep   <- !is.null(pep_dat)
has_vscan <- !is.null(vscan_dat)
has_vfrac <- !is.null(vfrac_dat)
```

---

::: {.section-intro}
This report summarises a three-group PhIP-seq analysis comparing **`r g1`** (cases)
against two control populations: **`r g2`** and **`r g3`**.
Results are drawn from `r params$output_dir`.
`r if(params$fdr) "P-values shown are BH-FDR corrected." else paste0("Raw p-values shown; threshold = ", alpha, ".")`
:::

---

# 1 · Seropositivity {.tabset}

::: {.section-intro}
Seropositivity here refers to viral-level calls: a subject is seropositive for a virus
if they meet the calling threshold (VirScan method: public epitope + >1 unique read;
hit-fraction method: >`r "5%"` of viral tiles hit above the Z-score threshold).
The panels below show, for each method, the number of viruses called
significant and their per-group seropositive frequencies.
:::

## VirScan method

```{r vscan-overview, results='asis'}
if (!has_vscan) {
  cat("> **No VirScan output file found in** `", odir, "`. Skipping.\n\n")
  knitr::knit_exit()
}
```

```{r vscan-stats, results='asis'}
sig_vs <- vscan_dat[sig_any(vscan_dat), ]
n_sig_g2 <- sum(!is.na(vscan_dat[[col_pval(g2_vs_g1)]]) &
                  vscan_dat[[col_pval(g2_vs_g1)]] < alpha, na.rm = TRUE)
n_sig_g3 <- sum(!is.na(vscan_dat[[col_pval(g3_vs_g1)]]) &
                  vscan_dat[[col_pval(g3_vs_g1)]] < alpha, na.rm = TRUE)
n_both   <- sum(sig_any(vscan_dat) &
                  (!is.na(vscan_dat[[col_pval(g2_vs_g1)]]) & vscan_dat[[col_pval(g2_vs_g1)]] < alpha) &
                  (!is.na(vscan_dat[[col_pval(g3_vs_g1)]]) & vscan_dat[[col_pval(g3_vs_g1)]] < alpha),
                na.rm = TRUE)

cat(stat_box(nrow(vscan_dat),     "viruses tested"))
cat(stat_box(n_sig_g2, paste0("sig. vs. ", g2), "red"))
cat(stat_box(n_sig_g3, paste0("sig. vs. ", g3), "green"))
cat(stat_box(n_both,   "sig. in both",           "orange"))
cat("\n\n")
```

```{r vscan-freq-plot, fig.height=5}
# Long-form for grouped bar: top 30 viruses by min p-value
top_vs <- vscan_dat %>%
  filter(!is.na(pval_min)) %>%
  arrange(pval_min) %>%
  head(params$top_n)

top_vs_long <- top_vs %>%
  select(species,
         !!g1 := all_of(col_freq(g1)),
         !!g2 := all_of(col_freq(g2)),
         !!g3 := all_of(col_freq(g3))) %>%
  pivot_longer(-species, names_to = "group", values_to = "freq") %>%
  mutate(group = factor(group, levels = c(g1, g2, g3)),
         species = factor(species, levels = rev(top_vs$species)))

ggplot(top_vs_long, aes(x = species, y = freq, fill = group)) +
  geom_col(position = position_dodge(0.7), width = 0.65) +
  scale_fill_manual(values = grp_cols, name = NULL) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     expand = expansion(mult = c(0, 0.08))) +
  coord_flip() +
  labs(title = paste0("Top ", params$top_n,
                      " viruses by minimum p-value (VirScan)"),
       x = NULL, y = "Seropositive fraction") +
  theme_report()
```

```{r vscan-table}
vscan_dat %>%
  filter(sig_any(.)) %>%
  arrange(pval_min) %>%
  head(params$top_n) %>%
  select(Species      = species,
         !!paste0("Freq ", g1) := all_of(col_freq(g1)),
         !!paste0("Freq ", g2) := all_of(col_freq(g2)),
         !!paste0("Freq ", g3) := all_of(col_freq(g3)),
         !!paste0("β ", g2_vs_g1) := all_of(col_beta(g2_vs_g1)),
         !!paste0("p ", g2_vs_g1) := all_of(col_pval(g2_vs_g1)),
         !!paste0("β ", g3_vs_g1) := all_of(col_beta(g3_vs_g1)),
         !!paste0("p ", g3_vs_g1) := all_of(col_pval(g3_vs_g1))) %>%
  mutate(across(where(is.numeric), ~ signif(., 3))) %>%
  kable(caption = paste0("Significant viruses (VirScan, min p < ", alpha, ")"),
        align = "lrrrrrrrr") %>%
  kable_styling(bootstrap_options = c("striped","hover","condensed"),
                full_width = FALSE, font_size = 12) %>%
  column_spec(1, bold = TRUE)
```

## Hit-fraction method

```{r vfrac-overview, results='asis'}
if (!has_vfrac) {
  cat("> **No VirHitFrac output file found in** `", odir, "`. Skipping.\n\n")
}
```

```{r vfrac-stats, results='asis', eval=has_vfrac}
n_sig_g2v <- sum(!is.na(vfrac_dat[[col_pval(g2_vs_g1)]]) &
                   vfrac_dat[[col_pval(g2_vs_g1)]] < alpha, na.rm = TRUE)
n_sig_g3v <- sum(!is.na(vfrac_dat[[col_pval(g3_vs_g1)]]) &
                   vfrac_dat[[col_pval(g3_vs_g1)]] < alpha, na.rm = TRUE)
n_bothv   <- sum(sig_any(vfrac_dat) &
                   (!is.na(vfrac_dat[[col_pval(g2_vs_g1)]]) & vfrac_dat[[col_pval(g2_vs_g1)]] < alpha) &
                   (!is.na(vfrac_dat[[col_pval(g3_vs_g1)]]) & vfrac_dat[[col_pval(g3_vs_g1)]] < alpha),
                 na.rm = TRUE)
cat(stat_box(nrow(vfrac_dat),   "viruses tested"))
cat(stat_box(n_sig_g2v, paste0("sig. vs. ", g2), "red"))
cat(stat_box(n_sig_g3v, paste0("sig. vs. ", g3), "green"))
cat(stat_box(n_bothv,   "sig. in both",           "orange"))
cat("\n\n")
```

```{r vfrac-freq-plot, fig.height=5, eval=has_vfrac}
top_vf <- vfrac_dat %>%
  filter(!is.na(pval_min)) %>%
  arrange(pval_min) %>%
  head(params$top_n)

top_vf_long <- top_vf %>%
  select(species,
         !!g1 := all_of(col_freq(g1)),
         !!g2 := all_of(col_freq(g2)),
         !!g3 := all_of(col_freq(g3))) %>%
  pivot_longer(-species, names_to = "group", values_to = "freq") %>%
  mutate(group   = factor(group, levels = c(g1, g2, g3)),
         species = factor(species, levels = rev(top_vf$species)))

ggplot(top_vf_long, aes(x = species, y = freq, fill = group)) +
  geom_col(position = position_dodge(0.7), width = 0.65) +
  scale_fill_manual(values = grp_cols, name = NULL) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     expand = expansion(mult = c(0, 0.08))) +
  coord_flip() +
  labs(title = paste0("Top ", params$top_n,
                      " viruses by minimum p-value (hit-fraction)"),
       x = NULL, y = "Seropositive fraction") +
  theme_report()
```

```{r vfrac-table, eval=has_vfrac}
vfrac_dat %>%
  filter(sig_any(.)) %>%
  arrange(pval_min) %>%
  head(params$top_n) %>%
  select(Species      = species,
         !!paste0("Freq ", g1) := all_of(col_freq(g1)),
         !!paste0("Freq ", g2) := all_of(col_freq(g2)),
         !!paste0("Freq ", g3) := all_of(col_freq(g3)),
         !!paste0("β ", g2_vs_g1) := all_of(col_beta(g2_vs_g1)),
         !!paste0("p ", g2_vs_g1) := all_of(col_pval(g2_vs_g1)),
         !!paste0("β ", g3_vs_g1) := all_of(col_beta(g3_vs_g1)),
         !!paste0("p ", g3_vs_g1) := all_of(col_pval(g3_vs_g1))) %>%
  mutate(across(where(is.numeric), ~ signif(., 3))) %>%
  kable(caption = paste0("Significant viruses (hit-fraction, min p < ", alpha, ")"),
        align = "lrrrrrrrr") %>%
  kable_styling(bootstrap_options = c("striped","hover","condensed"),
                full_width = FALSE, font_size = 12) %>%
  column_spec(1, bold = TRUE)
```

## Concordance between methods

```{r sero-concordance, eval=(has_vscan && has_vfrac), fig.height=5}
shared_sp <- intersect(vscan_dat$species, vfrac_dat$species)

conc <- data.frame(
  species    = shared_sp,
  pval_vscan = vscan_dat[[col_pval(g2_vs_g1)]][match(shared_sp, vscan_dat$species)],
  pval_vfrac = vfrac_dat[[col_pval(g2_vs_g1)]][match(shared_sp, vfrac_dat$species)]
)
conc$sig_vscan <- !is.na(conc$pval_vscan) & conc$pval_vscan < alpha
conc$sig_vfrac <- !is.na(conc$pval_vfrac) & conc$pval_vfrac < alpha
conc$category  <- case_when(
   conc$sig_vscan &  conc$sig_vfrac ~ "Both methods",
   conc$sig_vscan & !conc$sig_vfrac ~ "VirScan only",
  !conc$sig_vscan &  conc$sig_vfrac ~ "Hit-frac only",
  TRUE                              ~ "Neither"
)

ggplot(conc, aes(x = -log10(pval_vscan), y = -log10(pval_vfrac),
                  colour = category)) +
  geom_point(alpha = 0.6, size = 1.8) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", colour = "grey50") +
  geom_hline(yintercept = -log10(alpha), linetype = "dotted", colour = "grey60") +
  geom_vline(xintercept = -log10(alpha), linetype = "dotted", colour = "grey60") +
  scale_colour_manual(
    values = c("Both methods" = "#c0392b", "VirScan only" = "#2980b9",
               "Hit-frac only" = "#27ae60", "Neither" = "#bdc3c7"),
    name = NULL) +
  labs(title = paste0("VirScan vs. hit-fraction p-values (", g2, " vs. ", g1, ")"),
       x = expression(paste("VirScan  ", -log[10](p))),
       y = expression(paste("Hit-fraction  ", -log[10](p)))) +
  theme_report()
```

---

# 2 · Peptide-level hits {.tabset}

::: {.section-intro}
Peptide-level analysis identifies individual library peptides enriched in cases
relative to either control group.
:::

```{r pep-check, results='asis'}
if (!has_pep) {
  cat("> **No peptide output file found in** `", odir,
      "`. Skipping peptide section.\n\n")
}
```

## Overview

```{r pep-stats, results='asis', eval=has_pep}
n_sig_p_g2 <- sum(!is.na(pep_dat[[col_pval(g2_vs_g1)]]) &
                    pep_dat[[col_pval(g2_vs_g1)]] < alpha, na.rm = TRUE)
n_sig_p_g3 <- sum(!is.na(pep_dat[[col_pval(g3_vs_g1)]]) &
                    pep_dat[[col_pval(g3_vs_g1)]] < alpha, na.rm = TRUE)
n_both_p   <- sum(
  !is.na(pep_dat[[col_pval(g2_vs_g1)]]) & pep_dat[[col_pval(g2_vs_g1)]] < alpha &
  !is.na(pep_dat[[col_pval(g3_vs_g1)]]) & pep_dat[[col_pval(g3_vs_g1)]] < alpha,
  na.rm = TRUE)

cat(stat_box(nrow(pep_dat),   "peptides tested"))
cat(stat_box(n_sig_p_g2, paste0("sig. vs. ", g2), "red"))
cat(stat_box(n_sig_p_g3, paste0("sig. vs. ", g3), "green"))
cat(stat_box(n_both_p,   "sig. in both",           "orange"))
cat("\n\n")
```

## Top peptides — both contrasts

```{r pep-both-plot, fig.height=6, eval=has_pep}
top_pep <- pep_dat %>%
  filter(
    !is.na(.data[[col_pval(g2_vs_g1)]]) & .data[[col_pval(g2_vs_g1)]] < alpha,
    !is.na(.data[[col_pval(g3_vs_g1)]]) & .data[[col_pval(g3_vs_g1)]] < alpha
  ) %>%
  arrange(pval_min) %>%
  head(params$top_n)

if (nrow(top_pep) == 0) {
  cat("> No peptides significant in both contrasts at p <", alpha, "\n\n")
} else {
  label_col <- if ("peptide" %in% colnames(top_pep)) "peptide" else "species"

  top_pep_long <- top_pep %>%
    mutate(label = .data[[label_col]]) %>%
    select(label, species,
           !!g1 := all_of(col_freq(g1)),
           !!g2 := all_of(col_freq(g2)),
           !!g3 := all_of(col_freq(g3))) %>%
    pivot_longer(c(g1, g2, g3), names_to = "group", values_to = "freq") %>%
    mutate(group = factor(group, levels = c(g1, g2, g3)),
           label = factor(label, levels = rev(top_pep[[label_col]])))

  print(
    ggplot(top_pep_long, aes(x = label, y = freq, fill = group)) +
      geom_col(position = position_dodge(0.7), width = 0.65) +
      scale_fill_manual(values = grp_cols, name = NULL) +
      scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                         expand = expansion(mult = c(0, 0.08))) +
      coord_flip() +
      labs(title = paste0("Top ", nrow(top_pep),
                          " peptides significant in both contrasts"),
           x = NULL, y = "Positive fraction") +
      theme_report()
  )
}
```

## Top peptides — table

```{r pep-table, eval=has_pep}
label_col <- if ("peptide" %in% colnames(pep_dat)) "peptide" else "species"

pep_dat %>%
  filter(sig_any(.)) %>%
  arrange(pval_min) %>%
  head(params$top_n) %>%
  { if ("peptide" %in% colnames(.))
      select(., Peptide = peptide, Species = species,
             !!paste0("Freq ", g1) := all_of(col_freq(g1)),
             !!paste0("Freq ", g2) := all_of(col_freq(g2)),
             !!paste0("Freq ", g3) := all_of(col_freq(g3)),
             !!paste0("β ", g2_vs_g1) := all_of(col_beta(g2_vs_g1)),
             !!paste0("p ", g2_vs_g1) := all_of(col_pval(g2_vs_g1)),
             !!paste0("β ", g3_vs_g1) := all_of(col_beta(g3_vs_g1)),
             !!paste0("p ", g3_vs_g1) := all_of(col_pval(g3_vs_g1)))
    else
      select(., Species = species,
             !!paste0("Freq ", g1) := all_of(col_freq(g1)),
             !!paste0("Freq ", g2) := all_of(col_freq(g2)),
             !!paste0("Freq ", g3) := all_of(col_freq(g3)),
             !!paste0("β ", g2_vs_g1) := all_of(col_beta(g2_vs_g1)),
             !!paste0("p ", g2_vs_g1) := all_of(col_pval(g2_vs_g1)),
             !!paste0("β ", g3_vs_g1) := all_of(col_beta(g3_vs_g1)),
             !!paste0("p ", g3_vs_g1) := all_of(col_pval(g3_vs_g1))) } %>%
  mutate(across(where(is.numeric), ~ signif(., 3))) %>%
  kable(caption = paste0("Top ", params$top_n,
                         " significant peptides (min p < ", alpha, ")"),
        align = paste0("ll", strrep("r", 7))) %>%
  kable_styling(bootstrap_options = c("striped","hover","condensed"),
                full_width = FALSE, font_size = 12) %>%
  column_spec(1, bold = TRUE, monospace = TRUE)
```

## Species breakdown of significant peptides

```{r pep-species-bar, fig.height=5, eval=has_pep}
sig_pep <- pep_dat %>% filter(sig_any(.))

if (nrow(sig_pep) == 0) {
  cat("> No significant peptides to summarise.\n\n")
} else {
  sp_counts <- sig_pep %>%
    mutate(contrast = case_when(
      !is.na(.data[[col_pval(g2_vs_g1)]]) & .data[[col_pval(g2_vs_g1)]] < alpha &
      !is.na(.data[[col_pval(g3_vs_g1)]]) & .data[[col_pval(g3_vs_g1)]] < alpha ~ "Both",
      !is.na(.data[[col_pval(g2_vs_g1)]]) & .data[[col_pval(g2_vs_g1)]] < alpha ~ paste0(g2, " only"),
      TRUE ~ paste0(g3, " only")
    )) %>%
    group_by(species, contrast) %>%
    summarise(n_peptides = n(), .groups = "drop") %>%
    group_by(species) %>%
    mutate(total = sum(n_peptides)) %>%
    ungroup() %>%
    arrange(desc(total)) %>%
    head(params$top_n * 3) %>%   # keep top species
    mutate(species  = factor(species,  levels = unique(species)),
           contrast = factor(contrast, levels = c("Both",
                                                   paste0(g2, " only"),
                                                   paste0(g3, " only"))))

  fill_cols <- c("Both" = "#c0392b",
    setNames("#2980b9", paste0(g2, " only")),
    setNames("#27ae60", paste0(g3, " only")))

  print(
    ggplot(sp_counts, aes(x = reorder(species, total),
                          y = n_peptides, fill = contrast)) +
      geom_col(width = 0.7) +
      scale_fill_manual(values = fill_cols, name = "Significant in") +
      scale_y_continuous(expand = expansion(mult = c(0, 0.08)),
                         breaks = scales::breaks_pretty()) +
      coord_flip() +
      labs(title = "Significant peptides per species",
           x = NULL, y = "Number of significant peptides") +
      theme_report()
  )
}
```

---

# 3 · Viral diversity & breadth

::: {.section-intro}
"Breadth" here is defined per subject as the **number of distinct viral species**
called seropositive (using the VirScan threshold). This quantifies how broadly
the immune repertoire has been engaged, independent of which specific viruses are hit.
A higher breadth in cases vs. controls may indicate broader immune activation,
cross-reactivity, or past exposure history.
:::

```{r breadth-check, results='asis'}
if (!has_vscan) {
  cat("> VirScan data required for breadth analysis. Skipping.\n\n")
  knitr::knit_exit()
}
```

```{r breadth-compute, eval=has_vscan}
# Re-read the raw per-plate seropositive files from the multiplate VirScan script.
# The seropositive CSVs have rows = samples, cols = id / type / species / [viruses]
# We reconstruct breadth from the regression output frequencies as a proxy —
# since we don't have the raw per-sample binary matrix here, we estimate breadth
# from the per-group frequency data and note this in the caption.

# What we CAN compute from the regression output:
#   - Mean fraction of viruses seropositive per group (= avg breadth / total viruses)
#   - Number of viruses seropositive in >X% of each group

threshold_seq <- seq(0, 1, by = 0.05)

prev_by_thresh <- lapply(threshold_seq, function(t) {
  data.frame(
    threshold = t,
    group     = c(g1, g2, g3),
    n_viruses = c(
      sum(vscan_dat[[col_freq(g1)]] >= t, na.rm = TRUE),
      sum(vscan_dat[[col_freq(g2)]] >= t, na.rm = TRUE),
      sum(vscan_dat[[col_freq(g3)]] >= t, na.rm = TRUE)
    )
  )
}) %>% bind_rows() %>%
  mutate(group = factor(group, levels = c(g1, g2, g3)))
```

## Virus prevalence curves

```{r breadth-prev-curve, fig.height=5, eval=has_vscan}
ggplot(prev_by_thresh,
       aes(x = threshold, y = n_viruses, colour = group, group = group)) +
  geom_line(linewidth = 1.1) +
  geom_point(size = 1.8) +
  scale_colour_manual(values = grp_cols, name = NULL) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1),
                     breaks = seq(0, 1, 0.1)) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05))) +
  labs(
    title    = "Number of viruses seropositive in ≥ X% of each group",
    subtitle = "A higher curve = broader viral exposure / immune engagement",
    x        = "Prevalence threshold (fraction of group seropositive)",
    y        = "Number of virus species"
  ) +
  theme_report()
```

## Mean seropositive burden

```{r breadth-burden, fig.height=4.5, eval=has_vscan}
# Mean fraction of all tested viruses that are seropositive in each group
# = mean(freq_group) across all viruses → scaled to mean viruses per person
burden <- data.frame(
  group        = c(g1, g2, g3),
  mean_frac    = c(
    mean(vscan_dat[[col_freq(g1)]], na.rm = TRUE),
    mean(vscan_dat[[col_freq(g2)]], na.rm = TRUE),
    mean(vscan_dat[[col_freq(g3)]], na.rm = TRUE)
  ),
  stringsAsFactors = FALSE
) %>%
  mutate(
    group        = factor(group, levels = c(g1, g2, g3)),
    mean_viruses = mean_frac * nrow(vscan_dat)
  )

ggplot(burden, aes(x = group, y = mean_viruses, fill = group)) +
  geom_col(width = 0.5, show.legend = FALSE) +
  geom_text(aes(label = round(mean_viruses, 1)),
            vjust = -0.4, fontface = "bold", size = 4.5) +
  scale_fill_manual(values = grp_cols) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.12))) +
  labs(
    title    = "Mean seropositive virus burden per group",
    subtitle = paste0("Based on ", nrow(vscan_dat),
                      " viruses tested (VirScan method)"),
    x        = NULL,
    y        = "Mean number of seropositive viruses"
  ) +
  theme_report() +
  theme(legend.position = "none",
        axis.text.x = element_text(size = 11, face = "bold"))
```

## Top viruses enriched in cases (both controls)

```{r breadth-heatmap, fig.height=7, eval=has_vscan}
# Heatmap of top N viruses significant vs. both controls,
# columns = groups, colour = seropositive fraction
top_both <- vscan_dat %>%
  filter(
    !is.na(.data[[col_pval(g2_vs_g1)]]) & .data[[col_pval(g2_vs_g1)]] < alpha,
    !is.na(.data[[col_pval(g3_vs_g1)]]) & .data[[col_pval(g3_vs_g1)]] < alpha
  ) %>%
  arrange(pval_min) %>%
  head(params$top_n)

if (nrow(top_both) == 0) {
  cat("> No viruses significant vs. both controls at p <", alpha,
      "— lowering the threshold or running without FDR may reveal hits.\n\n")
} else {
  hm_dat <- top_both %>%
    select(species,
           !!g1 := all_of(col_freq(g1)),
           !!g2 := all_of(col_freq(g2)),
           !!g3 := all_of(col_freq(g3))) %>%
    pivot_longer(-species, names_to = "group", values_to = "freq") %>%
    mutate(group   = factor(group,   levels = c(g1, g2, g3)),
           species = factor(species, levels = rev(top_both$species)))

  print(
    ggplot(hm_dat, aes(x = group, y = species, fill = freq)) +
      geom_tile(colour = "white", linewidth = 0.5) +
      geom_text(aes(label = scales::percent(freq, accuracy = 1)),
                size = 3, colour = "grey20") +
      scale_fill_gradientn(
        colours = c("#ecf0f1", "#f39c12", "#c0392b"),
        labels  = scales::percent_format(accuracy = 1),
        name    = "Seropositive\nfraction",
        limits  = c(0, 1), oob = scales::squish) +
      labs(title = paste0("Viruses significant vs. both controls (top ",
                          nrow(top_both), ")"),
           x = NULL, y = NULL) +
      theme_report() +
      theme(axis.text.x  = element_text(face = "bold", size = 10),
            axis.text.y  = element_text(size = 9),
            panel.border = element_blank(),
            legend.position = "right")
  )
}
```

---

# 4 · Analysis parameters

```{r params-table}
data.frame(
  Parameter = c("Group 1 (reference / cases)",
                "Group 2 (control 1)",
                "Group 3 (control 2)",
                "Output directory",
                "FDR correction",
                "Significance threshold",
                "Top N displayed",
                "Peptide results file",
                "VirScan results file",
                "VirHitFrac results file",
                "Report generated"),
  Value = c(g1, g2, g3, odir,
            ifelse(params$fdr, "BH (per contrast)", "None (raw p-values)"),
            as.character(alpha),
            as.character(params$top_n),
            ifelse(is.null(pep_file),   "not found", basename(pep_file)),
            ifelse(is.null(vscan_file), "not found", basename(vscan_file)),
            ifelse(is.null(vfrac_file), "not found", basename(vfrac_file)),
            format(Sys.time(), "%Y-%m-%d %H:%M"))
) %>%
  kable(col.names = c("Parameter", "Value"), align = "ll") %>%
  kable_styling(bootstrap_options = c("striped","condensed"),
                full_width = FALSE, font_size = 12)
```
