---
title: "PhIP-seq Three-Group Combined Report"
subtitle: "Cross-condition summary across Z-score thresholds and sex strata"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    theme: flatly
    highlight: tango
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    toc_depth: 3
    self_contained: true
    df_print: paged
params:
  group1:        "PF Patient"
  group2:        "Endemic Control"
  group3:        "Non Endemic Control"
  output_dir:    "./"
  zscores:       "3.5,5,10"
  sexes:         ",M,F"
  pval_thresh:   0.05
  fdr:           true
  top_n:         20
  per_condition_subdir: "per_condition_reports"
---

```{css, echo=FALSE}
body { font-size: 14px; }
h1, h2, h3 { color: #2c3e50; }
.section-intro { color: #555; margin-bottom: 1em; font-style: italic; }
.stat-box {
  display: inline-block; padding: 12px 20px; margin: 6px;
  border-radius: 6px; text-align: center; min-width: 130px;
  background: #ecf0f1;
}
.stat-box .num { font-size: 1.8em; font-weight: bold; color: #2980b9; }
.stat-box .lbl { font-size: 0.85em; color: #7f8c8d; }
.stat-box.red   .num { color: #c0392b; }
.stat-box.green .num { color: #27ae60; }
.stat-box.orange .num { color: #d35400; }
.note { background: #fff8dc; border-left: 4px solid #f39c12;
        padding: 10px 14px; margin: 12px 0; }
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.width  = 10,
  fig.height = 5.5
)

pkgs <- c("data.table", "ggplot2", "dplyr", "tidyr", "knitr",
          "kableExtra", "scales", "stringr")
invisible(lapply(pkgs, function(p) {
  if (!requireNamespace(p, quietly = TRUE))
    stop(paste0("Install required package: ", p))
  library(p, character.only = TRUE)
}))

# ── parameters ────────────────────────────────────────────────────────────────
g1     <- params$group1
g2     <- params$group2
g3     <- params$group3
odir   <- params$output_dir
alpha  <- params$pval_thresh

# Parse comma-separated lists; preserve "" for "both sexes"
zscores <- trimws(strsplit(params$zscores, ",")[[1]])
sexes   <- trimws(strsplit(params$sexes,   ",")[[1]])
# strsplit drops trailing empties, so add back if the input starts/ends with ","
if (grepl("^,", params$sexes)) sexes <- c("", sexes)
if (grepl(",$", params$sexes)) sexes <- c(sexes, "")
sexes <- unique(sexes)

# Build the full grid of conditions
conditions <- expand.grid(zscore = zscores, sex = sexes,
                          stringsAsFactors = FALSE)
conditions$label <- paste0("Z=", conditions$zscore, ", sex=",
                            ifelse(nchar(conditions$sex) == 0,
                                   "both", conditions$sex))
conditions$sex_label <- ifelse(nchar(conditions$sex) == 0, "both",
                                conditions$sex)

g2_vs_g1 <- paste0(g2, "_vs_", g1)
g3_vs_g1 <- paste0(g3, "_vs_", g1)
col_freq <- function(g) paste0("freq_", g)
col_pval <- function(x) paste0("pval_", x)
col_beta <- function(x) paste0("beta_", x)

# ── file finder (mirrors per-condition Rmd's strict matcher) ──────────────────
find_csv <- function(prefix, zscore, sex) {
  zsex_pat <- paste0("-Z-", zscore, "-sex-", sex, "(-|\\.csv$)")
  hits <- list.files(odir, pattern = paste0(prefix, ".*", zsex_pat),
                     full.names = TRUE)
  hits <- hits[grepl("\\.csv$", hits) &
               !grepl("\\.gz$|\\.bz2$|\\.zip$|\\.tgz$", hits)]
  if (length(hits) == 0) return(NULL)
  hits <- hits[order(file.info(hits)$mtime, decreasing = TRUE)]
  hits[1]
}

read_one <- function(prefix, zscore, sex) {
  path <- find_csv(prefix, zscore, sex)
  if (is.null(path)) return(NULL)
  df <- tryCatch(
    data.frame(data.table::fread(path, sep = ",", header = TRUE),
               check.names = FALSE),
    error = function(e) NULL)
  if (is.null(df)) return(NULL)
  for (col in colnames(df))
    if (!(col %in% c("peptide", "species")))
      suppressWarnings({ df[[col]] <- as.numeric(df[[col]]) })
  if (params$fdr) {
    for (col in c(col_pval(g2_vs_g1), col_pval(g3_vs_g1)))
      if (col %in% colnames(df))
        df[[col]] <- p.adjust(df[[col]], method = "BH")
  }
  df$pval_min <- pmin(df[[col_pval(g2_vs_g1)]],
                      df[[col_pval(g3_vs_g1)]], na.rm = TRUE)
  df$file_path <- path
  df
}

# ── load all 9×3 datasets ─────────────────────────────────────────────────────
prefixes <- list(
  Peptide    = "Multiplate_Three_Group_Peptide_Comparison",
  VirScan    = "Multiplate_Three_Group_VirScan_Seropositivity_Comparison",
  VirHitFrac = "Multiplate_Three_Group_VirFrac_Seropositivity_Comparison"
)

data_grid <- list()
coverage <- data.frame()
for (i in seq_len(nrow(conditions))) {
  z <- conditions$zscore[i]; s <- conditions$sex[i]
  for (nm in names(prefixes)) {
    df <- read_one(prefixes[[nm]], z, s)
    key <- paste(nm, z, s, sep = "|")
    data_grid[[key]] <- df
    coverage <- rbind(coverage, data.frame(
      analysis = nm, zscore = z, sex = s,
      sex_label = ifelse(nchar(s) == 0, "both", s),
      label = conditions$label[i],
      found = !is.null(df),
      n_features = if (is.null(df)) NA_integer_ else nrow(df),
      n_sig_g2   = if (is.null(df)) NA_integer_
                   else sum(df[[col_pval(g2_vs_g1)]] < alpha, na.rm = TRUE),
      n_sig_g3   = if (is.null(df)) NA_integer_
                   else sum(df[[col_pval(g3_vs_g1)]] < alpha, na.rm = TRUE),
      n_sig_any  = if (is.null(df)) NA_integer_
                   else sum(df$pval_min < alpha, na.rm = TRUE),
      stringsAsFactors = FALSE
    ))
  }
}

# Locate per-condition reports if they were generated
per_cond_dir <- file.path(odir, params$per_condition_subdir)
find_per_condition_report <- function(z, s) {
  if (!dir.exists(per_cond_dir)) return(NA_character_)
  pat <- paste0("Three_Group_Summary_Report.*-Z-", z, "-sex-",
                ifelse(nchar(s) == 0, "both", s), "\\.html$")
  hits <- list.files(per_cond_dir, pattern = pat, full.names = FALSE)
  if (length(hits) == 0) NA_character_ else hits[1]
}

# ── shared palettes / theme ───────────────────────────────────────────────────
grp_cols <- c(setNames("#c0392b", g1),
              setNames("#2980b9", g2),
              setNames("#27ae60", g3))

theme_report <- function()
  theme_bw(base_size = 11) +
  theme(panel.grid.minor = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5),
        legend.position = "bottom")

stat_box <- function(n, label, cls = "") {
  sprintf(
    '<div class="stat-box %s"><div class="num">%s</div><div class="lbl">%s</div></div>',
    cls, format(n, big.mark = ","), label)
}
```

::: {.section-intro}
This report combines results from a three-group PhIP-seq analysis run across
**`r length(zscores)` Z-score threshold(s)** (`r paste(zscores, collapse = ", ")`)
and **`r length(sexes)` sex stratum/strata**
(`r paste(ifelse(nchar(sexes) == 0, "both", sexes), collapse = ", ")`),
yielding **`r nrow(conditions)`** condition combinations per analysis type.

Groups compared: **`r g1`** (cases) vs. **`r g2`** and **`r g3`**.
`r if(params$fdr) "P-values are BH-FDR corrected per condition." else paste0("Raw p-values used; threshold = ", alpha, ".")`

The combined view answers: **which hits are robust across thresholding and
stratification choices?** Features significant in one condition but not others
are likely sensitive to those choices; features significant in many are
the strongest candidates.
:::

---

# 1 · Coverage matrix

::: {.section-intro}
Which of the `r nrow(conditions) * 3` expected result files were located in
`r odir`? Missing files indicate runs that were not completed or used different
naming.
:::

```{r coverage-matrix, fig.height=2.5 + 0.5 * length(zscores), fig.width=10}
cov_long <- coverage %>%
  mutate(
    z_factor  = factor(zscore,    levels = zscores),
    s_factor  = factor(sex_label, levels = ifelse(nchar(sexes) == 0, "both", sexes)),
    fill_label = ifelse(found,
                        paste0(n_features, " feat.\n", n_sig_any, " sig."),
                        "MISSING")
  )

ggplot(cov_long, aes(x = s_factor, y = z_factor)) +
  geom_tile(aes(fill = found), colour = "white", linewidth = 1) +
  geom_text(aes(label = fill_label), size = 3, lineheight = 0.9) +
  facet_wrap(~ analysis, nrow = 1) +
  scale_fill_manual(values = c(`TRUE` = "#d5f5e3", `FALSE` = "#fadbd8"),
                    labels = c("Missing", "Found"), name = NULL) +
  scale_x_discrete(name = "Sex stratum") +
  scale_y_discrete(name = "Z-score threshold") +
  labs(title = "File coverage and significant feature counts") +
  theme_report() +
  theme(strip.background = element_rect(fill = "#34495e"),
        strip.text = element_text(colour = "white", face = "bold"))
```

```{r coverage-summary, results='asis'}
n_total   <- nrow(coverage)
n_found   <- sum(coverage$found)
n_missing <- n_total - n_found
cat(stat_box(n_total,   "expected files"))
cat(stat_box(n_found,   "files found",   "green"))
cat(stat_box(n_missing, "files missing", if (n_missing > 0) "red" else "green"))
cat("\n\n")
if (n_missing > 0) {
  miss <- coverage[!coverage$found,
                    c("analysis", "zscore", "sex_label")]
  cat('::: {.note}\n**Missing files** — the affected sections below will skip these conditions:\n\n')
  cat(paste0("- ", miss$analysis, ": Z=", miss$zscore,
             ", sex=", miss$sex_label, collapse = "\n"))
  cat("\n:::\n")
}
```

---

# 2 · Significant feature counts across conditions {.tabset}

::: {.section-intro}
Number of features reaching significance in each Z × sex combination.
Strong signal that's robust to thresholding should appear as a consistent
gradient or plateau across the grid; signal that's only present in one cell
is likely method-sensitive.
:::

```{r sig-heatmaps-helper, include=FALSE}
sig_heatmap <- function(analysis_name, col, title) {
  d <- coverage %>%
    filter(analysis == analysis_name) %>%
    mutate(z_factor = factor(zscore, levels = zscores),
           s_factor = factor(sex_label,
                             levels = ifelse(nchar(sexes) == 0, "both", sexes)))
  ggplot(d, aes(x = s_factor, y = z_factor, fill = .data[[col]])) +
    geom_tile(colour = "white", linewidth = 1) +
    geom_text(aes(label = ifelse(is.na(.data[[col]]), "—",
                                  format(.data[[col]], big.mark = ","))),
              size = 4, fontface = "bold", colour = "grey15") +
    scale_fill_gradientn(
      colours = c("#ecf0f1", "#f39c12", "#c0392b"),
      na.value = "#fadbd8", name = "n significant") +
    labs(title = title, x = "Sex stratum", y = "Z-score threshold") +
    theme_report()
}
```

## Peptide

```{r sig-pep, fig.height=3 + 0.5 * length(zscores)}
sig_heatmap("Peptide", "n_sig_any",
            "Peptides significant in at least one contrast (per condition)")
```

## VirScan

```{r sig-vs, fig.height=3 + 0.5 * length(zscores)}
sig_heatmap("VirScan", "n_sig_any",
            "VirScan viruses significant in at least one contrast (per condition)")
```

## VirHitFrac

```{r sig-vf, fig.height=3 + 0.5 * length(zscores)}
sig_heatmap("VirHitFrac", "n_sig_any",
            "Hit-fraction viruses significant in at least one contrast (per condition)")
```

## Summary table

```{r coverage-table}
coverage %>%
  mutate(`Z` = zscore, `Sex` = sex_label,
         `Found` = ifelse(found, "✓", "✗"),
         `Features` = ifelse(is.na(n_features), "—",
                              format(n_features, big.mark = ",")),
         `Sig. vs g2` = ifelse(is.na(n_sig_g2), "—",
                                 format(n_sig_g2, big.mark = ",")),
         `Sig. vs g3` = ifelse(is.na(n_sig_g3), "—",
                                 format(n_sig_g3, big.mark = ",")),
         `Sig. any`   = ifelse(is.na(n_sig_any), "—",
                                 format(n_sig_any, big.mark = ","))) %>%
  select(Analysis = analysis, Z, Sex, Found, Features,
         `Sig. vs g2`, `Sig. vs g3`, `Sig. any`) %>%
  arrange(Analysis, Z, Sex) %>%
  kable(align = "lllcrrrr") %>%
  kable_styling(bootstrap_options = c("striped","hover","condensed"),
                full_width = FALSE, font_size = 11) %>%
  column_spec(1, bold = TRUE)
```

---

# 3 · Cross-condition robustness {.tabset}

::: {.section-intro}
For each feature (peptide / virus), in how many of the `r nrow(conditions)`
conditions was it significant? A feature significant in many conditions is
robust to threshold and sex choices; one significant in only one or two
conditions is method-sensitive and should be interpreted with caution.

The "n conditions" tally is more honest than a global multi-condition FDR
correction here, since the conditions are sensitivity analyses of the same
underlying question rather than independent tests of separate hypotheses.
:::

```{r robust-helper, include=FALSE}
# For each analysis type, build a long table of significant features ×
# condition, then count how many conditions each feature appears in.
build_robustness <- function(analysis_name, id_col) {
  rows <- list()
  for (i in seq_len(nrow(conditions))) {
    z <- conditions$zscore[i]; s <- conditions$sex[i]
    key <- paste(analysis_name, z, s, sep = "|")
    df <- data_grid[[key]]
    if (is.null(df)) next
    if (!(id_col %in% colnames(df))) next
    sig <- df[!is.na(df$pval_min) & df$pval_min < alpha,
              c(id_col, "pval_min", col_pval(g2_vs_g1), col_pval(g3_vs_g1))]
    if (nrow(sig) == 0) next
    sig$condition <- conditions$label[i]
    sig$sig_g2    <- !is.na(sig[[col_pval(g2_vs_g1)]]) &
                      sig[[col_pval(g2_vs_g1)]] < alpha
    sig$sig_g3    <- !is.na(sig[[col_pval(g3_vs_g1)]]) &
                      sig[[col_pval(g3_vs_g1)]] < alpha
    rows[[length(rows) + 1]] <- sig
  }
  if (length(rows) == 0) return(NULL)
  do.call(rbind, rows)
}

robustness_summary <- function(long_df, id_col) {
  if (is.null(long_df) || nrow(long_df) == 0) return(NULL)
  long_df %>%
    group_by(.data[[id_col]]) %>%
    summarise(
      n_conditions   = n_distinct(condition),
      n_sig_vs_g2    = sum(sig_g2),
      n_sig_vs_g3    = sum(sig_g3),
      n_sig_both     = sum(sig_g2 & sig_g3),
      min_pval       = min(pval_min, na.rm = TRUE),
      .groups        = "drop"
    ) %>%
    arrange(desc(n_conditions), min_pval)
}

robust_bar <- function(summary_df, title) {
  if (is.null(summary_df) || nrow(summary_df) == 0) {
    return(ggplot() + theme_void() +
           labs(title = paste(title, "— no significant features")))
  }
  counts <- summary_df %>%
    count(n_conditions, name = "n_features") %>%
    arrange(n_conditions) %>%
    mutate(robust = n_conditions >= ceiling(nrow(conditions) / 2))
  ggplot(counts, aes(x = factor(n_conditions), y = n_features, fill = robust)) +
    geom_col(width = 0.7) +
    geom_text(aes(label = format(n_features, big.mark = ",")),
              vjust = -0.4, fontface = "bold", size = 3.5) +
    scale_fill_manual(values = c(`TRUE` = "#27ae60", `FALSE` = "#bdc3c7"),
                      labels = c(paste0("< ", ceiling(nrow(conditions) / 2),
                                        " conditions"),
                                 paste0("\u2265 ", ceiling(nrow(conditions) / 2),
                                        " conditions")),
                      name = NULL) +
    scale_y_continuous(expand = expansion(mult = c(0, 0.12))) +
    labs(title    = title,
         subtitle = paste0("Total conditions = ", nrow(conditions)),
         x        = "Number of conditions where feature was significant",
         y        = "Number of features") +
    theme_report()
}
```

## Peptide

```{r robust-pep, fig.height=5}
pep_long <- build_robustness("Peptide",
                              if (any(sapply(data_grid, function(d)
                                "peptide" %in% colnames(d))))
                                "peptide" else "species")
id_col_pep <- ifelse(any(sapply(data_grid, function(d)
                          "peptide" %in% colnames(d))), "peptide", "species")
pep_summary <- robustness_summary(pep_long, id_col_pep)
robust_bar(pep_summary, "Peptide robustness")
```

```{r robust-pep-table}
if (!is.null(pep_summary) && nrow(pep_summary) > 0) {
  pep_summary %>%
    head(params$top_n) %>%
    mutate(min_pval = signif(min_pval, 3)) %>%
    rename(Feature        = !!id_col_pep,
           `# conditions` = n_conditions,
           `# vs g2`      = n_sig_vs_g2,
           `# vs g3`      = n_sig_vs_g3,
           `# both`       = n_sig_both,
           `min p`        = min_pval) %>%
    kable(caption = paste0("Top ", params$top_n,
                           " most robust peptides"),
          align = "lrrrrr") %>%
    kable_styling(bootstrap_options = c("striped","hover","condensed"),
                  full_width = FALSE, font_size = 12) %>%
    column_spec(1, bold = TRUE, monospace = (id_col_pep == "peptide"))
} else {
  cat("No significant peptides in any condition.\n")
}
```

## VirScan

```{r robust-vs, fig.height=5}
vs_long <- build_robustness("VirScan", "species")
vs_summary <- robustness_summary(vs_long, "species")
robust_bar(vs_summary, "VirScan virus robustness")
```

```{r robust-vs-table}
if (!is.null(vs_summary) && nrow(vs_summary) > 0) {
  vs_summary %>%
    head(params$top_n) %>%
    mutate(min_pval = signif(min_pval, 3)) %>%
    rename(Species        = species,
           `# conditions` = n_conditions,
           `# vs g2`      = n_sig_vs_g2,
           `# vs g3`      = n_sig_vs_g3,
           `# both`       = n_sig_both,
           `min p`        = min_pval) %>%
    kable(caption = paste0("Top ", params$top_n,
                           " most robust VirScan viruses"),
          align = "lrrrrr") %>%
    kable_styling(bootstrap_options = c("striped","hover","condensed"),
                  full_width = FALSE, font_size = 12) %>%
    column_spec(1, bold = TRUE)
} else {
  cat("No significant VirScan viruses in any condition.\n")
}
```

## VirHitFrac

```{r robust-vf, fig.height=5}
vf_long <- build_robustness("VirHitFrac", "species")
vf_summary <- robustness_summary(vf_long, "species")
robust_bar(vf_summary, "Hit-fraction virus robustness")
```

```{r robust-vf-table}
if (!is.null(vf_summary) && nrow(vf_summary) > 0) {
  vf_summary %>%
    head(params$top_n) %>%
    mutate(min_pval = signif(min_pval, 3)) %>%
    rename(Species        = species,
           `# conditions` = n_conditions,
           `# vs g2`      = n_sig_vs_g2,
           `# vs g3`      = n_sig_vs_g3,
           `# both`       = n_sig_both,
           `min p`        = min_pval) %>%
    kable(caption = paste0("Top ", params$top_n,
                           " most robust hit-fraction viruses"),
          align = "lrrrrr") %>%
    kable_styling(bootstrap_options = c("striped","hover","condensed"),
                  full_width = FALSE, font_size = 12) %>%
    column_spec(1, bold = TRUE)
} else {
  cat("No significant hit-fraction viruses in any condition.\n")
}
```

---

# 4 · Method concordance across conditions

::: {.section-intro}
For features significant in at least one condition, how often does the
result agree between the VirScan and hit-fraction calling methods? Strong
concordance means either method would have led to the same conclusion;
weak concordance suggests the call is sensitive to how seropositivity is
defined.
:::

```{r method-concord, fig.height=5}
# For each Z/sex condition, intersect VirScan and VirHitFrac significant species
concord <- list()
for (i in seq_len(nrow(conditions))) {
  z <- conditions$zscore[i]; s <- conditions$sex[i]
  vs <- data_grid[[paste("VirScan",    z, s, sep = "|")]]
  vf <- data_grid[[paste("VirHitFrac", z, s, sep = "|")]]
  if (is.null(vs) || is.null(vf)) next
  vs_sig <- vs$species[!is.na(vs$pval_min) & vs$pval_min < alpha]
  vf_sig <- vf$species[!is.na(vf$pval_min) & vf$pval_min < alpha]
  shared <- intersect(vs_sig, vf_sig)
  concord[[length(concord) + 1]] <- data.frame(
    condition  = conditions$label[i],
    zscore     = z,
    sex_label  = ifelse(nchar(s) == 0, "both", s),
    only_vs    = length(setdiff(vs_sig, vf_sig)),
    only_vf    = length(setdiff(vf_sig, vs_sig)),
    both       = length(shared)
  )
}
if (length(concord) > 0) {
  concord_df <- do.call(rbind, concord) %>%
    pivot_longer(c(only_vs, only_vf, both),
                 names_to = "category", values_to = "n") %>%
    mutate(category = factor(category,
                              levels = c("only_vs", "both", "only_vf"),
                              labels = c("VirScan only", "Both methods",
                                         "Hit-fraction only")))

  ggplot(concord_df, aes(x = condition, y = n, fill = category)) +
    geom_col(width = 0.7) +
    scale_fill_manual(values = c("VirScan only"      = "#2980b9",
                                  "Both methods"      = "#c0392b",
                                  "Hit-fraction only" = "#27ae60"),
                      name = NULL) +
    scale_y_continuous(expand = expansion(mult = c(0, 0.08))) +
    labs(title = "Significant virus overlap: VirScan vs. hit-fraction",
         x = NULL, y = "Number of significant viruses") +
    theme_report() +
    theme(axis.text.x = element_text(angle = 30, hjust = 1))
} else {
  cat("Not enough paired VirScan / hit-fraction data to assess concordance.\n")
}
```

---

# 5 · Per-condition reports

::: {.section-intro}
Individual reports for each Z × sex combination provide the full breakdown
(top hits, frequency tables, method concordance, breadth analysis) for that
specific condition.
:::

```{r per-condition-links, results='asis'}
links <- data.frame(
  Condition = character(0), Report = character(0),
  stringsAsFactors = FALSE
)
for (i in seq_len(nrow(conditions))) {
  z <- conditions$zscore[i]; s <- conditions$sex[i]
  rep_name <- find_per_condition_report(z, s)
  link <- if (is.na(rep_name)) {
    "_(not generated)_"
  } else {
    sprintf('<a href="%s/%s" target="_blank">Open report</a>',
            params$per_condition_subdir, rep_name)
  }
  links <- rbind(links, data.frame(
    Condition = conditions$label[i], Report = link,
    stringsAsFactors = FALSE))
}
kable(links, escape = FALSE, align = "ll") %>%
  kable_styling(bootstrap_options = c("striped","condensed"),
                full_width = FALSE, font_size = 12) %>%
  column_spec(1, bold = TRUE)
```

---

# 6 · Analysis parameters

```{r params-table}
data.frame(
  Parameter = c("Group 1 (cases)",
                "Group 2 (control 1)",
                "Group 3 (control 2)",
                "Z-score thresholds",
                "Sex strata",
                "Total conditions",
                "Output directory",
                "Per-condition subdir",
                "FDR correction",
                "Significance threshold",
                "Top N displayed",
                "Report generated"),
  Value = c(g1, g2, g3,
            paste(zscores, collapse = ", "),
            paste(ifelse(nchar(sexes) == 0, "both", sexes), collapse = ", "),
            as.character(nrow(conditions)),
            odir, params$per_condition_subdir,
            ifelse(params$fdr, "BH (per contrast, per condition)",
                   "None (raw p-values)"),
            as.character(alpha),
            as.character(params$top_n),
            format(Sys.time(), "%Y-%m-%d %H:%M"))
) %>%
  kable(align = "ll") %>%
  kable_styling(bootstrap_options = c("striped","condensed"),
                full_width = FALSE, font_size = 12)
```
